Crystals

### 2017-03-08 doc/ms.tex
Narrow and wide gaussian sections

\subsection{The narrow spikes}
I assumed that there is some number $N_{\rm narrow}$ of narrow spikes,
with central positions $X_1, X_2, ..., X_{N, \rm narrow}$, amplitudes
$A_1, A_2, ..., A_{N, \rm narrow}$, and widths
$W_1, W_2, ..., W_{N, \rm narrow}$. The total shape contributed by the
narrow spikes is a sum of $N_{\rm narrow}$ gaussians:
\begin{align}
f_{\rm narrow}(\x; \params_{\rm narrow}) &=
    \sum_{i=1}^{N_{\rm narrow}} A_i
                        \exp\left[-\frac{1}{2W_i^2}\left(x - X_i\right)^2\right]
\end{align}

\subsection{The wide `spikes'}

\subsection{Prior probability distributions}

The joint prior distribution for the hyperparameters, parameters, and data,
is written $p(\hypers, \params, \data | \info)$, and is usually factorised
in this way:
\begin{align}
p(\hypers, \params, \data | \info) &=
    p(\hypers | \info)p(\params | \hypers, \info)
    p(\data | \params, \hypers, \info)\\
    &= p(\hypers | \info)p(\params | \hypers, \info)
    p(\data | \params, \info)
\end{align}
where the first step is true in general by the product rule, and the second
step assumes that knowing the parameters would make the hyperparameters
irrelevant when predicting what data would be observed.

>>>>

\subsection{The narrow spikes}
I assumed that there is some number $N_{\rm narrow}$ of narrow spikes,
each of which has a gaussian shape. The $i$th narrow spike is parameterised
by its central position $X_{i, \rm narrow}$,
amplitude $A_{i, \rm narrow}$, and width $A_{i, \rm narrow}$.
The parameter vector for narrow spikes is
\begin{align}
\params_{\rm narrow} &=
  \{N_{\rm narrow}, X_1, X_2, ..., X_{N, \rm narrow},
    A_1, A_2, ..., A_{N, \rm narrow},
    W_1, W_2, ..., W_{N, \rm narrow}\}
\end{align}
and the total shape contributed by the
narrow spikes is a sum of the $N_{\rm narrow}$ gaussians:
\begin{align}
f_{\rm narrow}(\x; \params_{\rm narrow}) &=
    \sum_{i=1}^{N_{\rm narrow}} A_{i, \rm narrow}
 \exp\left[-\frac{1}{2W_{i, \rm narrow}^2}\left(x - X_{i, \rm narrow}\right)^2\right].
\end{align}

\subsection{The wide component}
The wide component is also composed of gaussians, like the narrow spikes.
In fact, the only real difference is the prior distributions for the positions,
amplitudes, and widths, given in Section~\ref{sec:priors}.

There is some number $N_{\rm wide}$ of gaussians in the wide component.
The $i$th gaussian is parameterised
by its central position $X_{i, \rm wide}$,
amplitude $A_{i, \rm wide}$, and width $A_{i, \rm wide}$.
The parameter vector for wide gaussians is
\begin{align}
\params_{\rm wide} &=
  \{N_{\rm wide}, X_1, X_2, ..., X_{N, \rm wide},
    A_1, A_2, ..., A_{N, \rm wide},
    W_1, W_2, ..., W_{N, \rm wide}\}
\end{align}
and the total shape contributed by the
wide component is a sum of the $N_{\rm wide}$ gaussians:
\begin{align}
f_{\rm wide}(\x; \params_{\rm wide}) &=
    \sum_{i=1}^{N_{\rm wide}} A_{i, \rm wide}
 \exp\left[-\frac{1}{2W_{i, \rm wide}^2}\left(x - X_{i, \rm wide}\right)^2\right].
\end{align}

\subsection{Prior probability distributions}\label{sec:priors}
The joint prior distribution for the hyperparameters, parameters, and data,
is written $p(\hypers, \params, \data | \info)$, and is usually factorised
in this way:
\begin{align}
p(\hypers, \params, \data | \info) &=
    p(\hypers | \info)p(\params | \hypers, \info)
    p(\data | \params, \hypers, \info)\\
    &= p(\hypers | \info)p(\params | \hypers, \info)
    p(\data | \params, \info)
\end{align}
where the first step is true in general by the product rule, and the second
step assumes that knowing the parameters would make the hyperparameters
irrelevant when predicting what data would be observed.
